\begin{thebibliography}{99}
	
	%thesis
	\bibitem{takano} 
	 高野健太郎, 大村賢悟, 柴田博仁: ``短編小説の読みにおける紙の書籍と電子書籍端末の比較,'' 情報処理学会第141回HCI研究会, Vol. 141, No. 4, pp.1--8 (Jan. 2011).
	
	\bibitem{shibata} 
	柴田博仁, 大村賢悟: ``答えを探す読みにおける紙の書籍と電子書籍端末の比較,'' 情報処理学会第141回HCI研究会, Vol. 141, No. 5, pp. 1--8 (Jan. 2011).
	
	 \bibitem{pablo}
	 P. Delgado, C. Vargas, R. Ackerman, and L. Salmer\'on: ``Don't Throw Away Your Printed Books: A Meta-analysis on the Effects of Reading Media on Reading Comprehension,'' {\it Journal of Educational Research Review}, Vol. 25, pp. 23--38 (Nov. 2018).
	 
	 \bibitem{inagawa1}
	稲川暢浩, 藤波香織: ``読書体験を豊かにするための本の拡張に関する研究,'' 情報処理学会第70回全国大会, pp. 131--132 (Mar. 2008).
	 
	 \bibitem{inagawa2}
	稲川暢浩, 藤波香織: ``読書中に低い妨害感で効果的に付加情報を伝達するための情報提示方法,'' 情報処理学会第135回HCI研究会, Vol. 2009, No. 12, pp. 1--8 (Dec. 2009).
	 
	 \bibitem{hashimoto}
	 橋本直己, 櫻井淳一: ``インタラクティブなプロジェクションマッピングの実現,'' 映像情報メディア学会誌, Vol. 67, No. 2, pp. 60--63 (Jan. 2013).
	
	\bibitem{isogaki}
	磯垣広野, K. S. Kyung, 澤野知佳, 福井 悠, 小林孝浩, 鈴木宣也, 関口敦仁: ``可動鏡を使ったマルチプロジェクションシステム -Ptolemy-,'' 情報処理学会シンポジウム論文集, Vol. 2007, No. 4, pp. 85--86 (Mar. 2008).
	
	\bibitem{doi}
	土井麻由佳, 宮下芳明: ``プロジェクションマッピングによる箏への演奏提示,'' 第23回インタラクティブシステムとソフトウェアに関するワークショップ論文集(WISS 2015), pp. 181--182 (Feb. 2015).
	
	
	\bibitem{gupta}
	S. Gupta and C. Jaynes: ``The Universal Media Book: Tracking and Augmenting Moving Surfaces with Projected Information,'' {\it Proc. of the ACM International Symposium on Mixed and Augmented Reality (ISMAR 2006)}, pp. 177--180 (Oct. 2006).
	
	\bibitem{suzuki}
	鈴木若菜, 竹田一貴, 外山託海, 黄瀬浩一: ``プロジェクタを用いた情報投影による印刷文書へのインタラクティブ性の付加,'' 電子情報通信学会技術研究報告, Vol. 111, No. 317, pp. 69--74 (Nov. 2011).
	
	\bibitem{ota}
	太田脩平, 寺田 努, 塚本昌彦: ``装着型プロジェクタと可動鏡による周辺状況を考慮した映像投影手法,'' エンタテインメントコンピューティングシンポジウム (EC 2012) 論文集, Vol. 2012, No. 1,  pp.1--7 (Mar. 2012).
	
	\bibitem{pranav}
	P. Mistry, P. Maes, and L. Chang: ``WUW - Wear Ur World - A Wearable Gestural Interface,'' {\it Proc. of the ACM International Conference on Human Factors in Computing Systems Extended Abstracts (CHI EA 2010)}, pp. 4111--4116 (Apr. 2009).
	
	\bibitem{chris}
	C. Harrison, H. Benko, and A. D. Wilson: ``OmniTouch: Wearable Multitouch Interaction Everywhere,'' {\it Proc. of the ACM symposium on User interface software and technology (UIST '11)}, pp. 441--450 (Oct. 2011).
	
	\bibitem{christian}
	C. Winkler, M. Broscheit, and E. Rukzio: ``NaviBeam: Indoor Assistance and Navigation for Shopping Malls through Projector Phones,'' {\it Proc. of the ACM Conference on Human Factors in Computing Systems (CHI 2011)}, (Jan. 2011).
	
	
	 \bibitem{karitsuka}
	  狩塚俊和, 佐藤宏介: ``プロジェクタ投影型ウェアラブル複合現実感システム, 情報処理学会研究報告コンピュータビジョンとイメージメディア (CVIM), Vol. 104, pp. 141--146 (Sep. 2003).
	  
	\bibitem{leap}LeapMotion, \url{https://www.leapmotion.com/ja/}.
	
	\bibitem{opencv}OpenCV, \url{https://opencv.org/}.
	
	\bibitem{google}Google Cloud Vision API, \url{https://cloud.google.com/vision/}.
	
	\bibitem{wikipedia}Wikipedia, \url{https://ja.wikipedia.org/wiki/}.
			
	\bibitem{mecab} 
	MeCab: MeCab: Yet Another Part-of-Speech and Morphological Analyzer,  \url{http://taku910.github.io/mecab/}.
	
	\bibitem{morimi}森見登美彦: 夜は短し歩けよ乙女, 角川書店 (2006).

	
\end{thebibliography}